STA302 Fall 2024 Final Project Part 1: Research Proposal and Data Introduction

### 2024-10-02 final_paper/paper.qmd
Polished preliminary results

# Preliminary Results (300 words)

@@

\newpage

>>>>

@@

\newpage  
# Preliminary Results (300 words)  
Our model demonstrates the relationship between the New Housing Price Index (NHPI) and various predictors, such as detached absorption and unabsorbed homes, homes starting construction, completed constructions, and rate hikes. To start, we will discuss the intercept, which is 88.52 when all predictors are zero. This serves as a baseline for evaluating the effects of other predictors.

The first predictor is detached absorption. For each additional home sold in a quarter, the expected decrease in the NHPI is 0.0227 points. In contrast, unabsorbed homes cause an increase of 0.005315 points in the NHPI. New homes beginning construction have a minimal impact, with a 0.0009611 point increase in the NHPI for every home that starts construction. Meanwhile, completed homes have a greater impact, with a 0.002977 point increase. Lastly, rate hikes have the most significant impact: when there is a rate increase, the NHPI decreases by 13.41 points.  
\newpage
